The Sub-Millimetre User Reduction Facility: an iterative map-maker for SCUBA-2

### 2011-03-11 smurf_paper.tex
add section about magnetic field pickup

\subsubsection{Magnetic field pickup}
Show that it occasionally appears in the dark squids.

>>>>

\subsubsection{Magnetic field pickup}
\label{sec:magpickup}

An additional noise source that appears to be significant in only a
small subset of the S2SRO data is magnetic field pickup. Since the
bolometer signals are ultimately detected through the amplification of
magnetic fields, any additional changing fields within the cryostat
will also be detected.

An example of an observation where pickup appears to be significant is
shown in Fig.~\ref{fig:magpickup}. The time-series for two
450\,\micron\ bolometers in the same column (not flatfielded) show
that there is a strong signal with a similar shape, but opposite
signs. This behaviour is seen across the entire array. The dark squid
signal for the same columns exhibits a similar shape and
amplitude. Since the dark squid has no thermal absorber or TES
attached to it, this observed signal is not likely to be optical or
thermal in nature (although there can be some crosstalk with the
bolometers...). It is also for this reason that the higher-frequency
noise that appears in the bolometer data (thermal) does not appear in
the dark squid, leading to a significantly higher \snr. The sign of
such a signal is expected to be random in the bolometer time-series
(ask detector person for an explanation).

\begin{figure}
\centering
\includegraphics[width=\linewidth]{magpickup.pdf}
\caption{Evidence for significant magnetic field pickup for
  observation 20100228\_00016.  The top panel shows two un-flatfielded
  (but mean-subtracted) bolometer time-series from the same column,
  with a 200 sample boxcar smooth (approximately 1\,s), illustrating
  that they are dominated by a similar signal with opposite signs. The
  second panel shows the dark squid signal for the column, also
  mean-subtracted and with the same boxcar smooth. The bottom panel
  shows the azimuthal and elevation offsets from the map centre. For
  reference, the mean azimuth was 171.9\,deg, and the mean elevation
  68.0\,deg. Only the azimuthal signal appears to be correlated with
  the dark squids and bolometer signals, which suggests a magnetic
  field stationary with respect to the telescope dome as the source,
  since its direction with respect to the cryostat only changes with
  azimuthal motion.}
\label{fig:magpickup}
\end{figure}

The telescope pointing offsets for this approximately 0.5\,deg
diameter scan are also shown in Fig.~\ref{fig:magpickup}. Since the
phase of the azimuth offsets from the map centre in this scan pattern
slowly drifts with respect to the elevation offsets, it is clear that
the bolometer and dark squid signals are detecting a noise source that
is correlated only with the azimuthal motion and \emph{not} the
elevation. This behaviour would be expected if if there were a strong
magnetic field fixed with respect to the telescope dome (i.e., the
earth's magnetic field). Since SCUBA-2 is mounted on a Nasmyth
platform, only azimuthal motion will change the effective direction of
such a field with respect to the cryostat. It is also worth noting
that the absolute azimuth of the telescope was close to 180\,deg
(i.e., nearly due-south). We suspect that this observing
configuration, combined with the large amplitude of the scan, may have
conspired to produce these large signals.
